---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
devtools::load_all()
```
# Post estimation for GLMs in R

[![Travis build status](https://travis-ci.org/josherrickson/postr.svg?branch=master)](https://travis-ci.org/josherrickson/postr)

[![Coverage status](https://codecov.io/gh/josherrickson/postr/branch/master/graph/badge.svg)](https://codecov.io/github/josherrickson/postr?branch=master)

After fitting a logistic model in R using `glm`, getting classification rates, ROC curves and AUCs are non-trivial - they're easy to do, but require coding manually every time.

The `postr` package simplifies this.

```{r}
data(mtcars)
m <- glm(vs ~ gear + mpg, data = mtcars, family = binomial)
```

All functions are prefaced by `postr_` (aliased with `pr_`) to simplify the names without worrying about conflicts with other packages. For example,

```{r}
pr_classtable(m, threshold = .4)
pr_sensitivity(m, threshold = .4)
pr_AUC(m)
```

```{r, dpi = 300}
pr_ROC(m)
```

